---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statcanopener

<!-- badges: start -->
[![R build status](https://github.com/tweed1e/statcanopener/workflows/R-CMD-check/badge.svg)](https://github.com/tweed1e/statcanopener/actions)
<!-- badges: end -->

Statcanopener provides a lightweight wrapper for [Statistics 
Canada's Web Data Service](https://www.statcan.gc.ca/eng/developers/wds). With 
it, you can build Statcan's API queries into your packages, reporting workflows 
or Shiny apps.

(Do not use API between 12:00 midnight and 8:30AM EST lol.)

## Installation

<!-- You can install the released version of statcanopener from [CRAN](https://CRAN.R-project.org) with: -->

You can install the development version of statcanopener from [github](https://github/tweed1e/statcanopener) with:

``` r
# install.packages("remotes")
remotes::install_github("tweed1e/statcanopener)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(statcanopener)

# Get metadata for product ID 35100003
result <- getCubeMetadata(35100003) # returns httr response object
content <- httr::content(result) # extract content of response

str(content[[1]], max.level = 2)
```


## Related packages

This package was inspired by the [cansim](https://github.com/mountainMath/cansim) package, which includes this functionality
and much more. This is intended to be a bare bones, non-opinionated wrapper for the 
web data service, rather than a full-fledged end-user API access package. (E.g., 
this won't have a function to automatically scale from millions of $ to $.)




